---
title: "WORKSHEET 3"
author: "Niel Andrew Callanga"
date: "2022-10-23"
output:
  html_document: default
  pdf_document: default
---

Using Vectors
\hfill\break
1. There is a built-in vector LETTERS contains the uppercase letters of the 
 alphabet and letters which contains the lowercase letters of the alphabet.
  
  LETTERS <- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J", "K", "L", "M", 
             "N", "O", "P", "Q", "R", "S", "T", "U", "V", "W", "X", "Y", "Z")

  
  letters <- c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j", "k", "l", "m", 
             "n", "o", "p", "q", "r", "s", "t", "u", "v", "w", "x", "y", "z")

Based on the above vector LETTERS:
  a. You need to produce a vector that contains the first 11 letters.
```{r , include = TRUE}
   
    LET <- LETTERS[1:11]
    LET
```
  

  b. Produce a vector that contains the odd numbered letters.
```{r , include = TRUE}
    
    LET1 <- LETTERS[1:26 %% 2 !=0]
    LET1
```
 
    
  c. Produce a vector that contains the vowels
```{r , include = TRUE}
    
    LET2 <- LETTERS[c(1, 5, 9, 15, 21)]
    LET2
```
  
    
Based on the above vector letters:
  d. Produce a vector that contains the last 5 lowercase letters.
```{r , include = TRUE}
    let <- letters[22:26]
    let
```
 
    
  e. Produce a vector that contains letters between 15 to 24 letters in 
  lowercase.
```{r , include = TRUE}
    let1 <- letters[15:24]
    let1
```

  
2. Create a vector with the average temperatures in April for Tuguegarao City,
    Manila, Iloilo City, Tacloban, Samal Island, and Davao City. The average
    temperatures in Celcius are 42, 39, 34, 34, 30, and 27 degrees.
    
  a. What is the R code and its result for creating a character vector for
  the city/town of Tuguegarao City, Manila, Iloilo City, Tacloban, Samal 
  Island, and Davao City? Name the object as city. The names should follow 
  the same order as in the instruction.
```{r , include = TRUE}
    city <- c("Tuguegarao City", "Manila", "Iloilo City", "Tacloban", 
    "Samal Island", "Davao City")
    city
```
  
  b. The average temperatures in Celcius are 42, 39, 34, 34, 30, and 27
  degrees. Name the object as temp. Write the R code and its output. Numbers 
  should also follow what is in the instruction.
```{r , include = TRUE}
    temp <- c(42, 39, 34, 34, 30, 27)
    temp
```
  
    
  c. Associate the temperature temp with the city by using names() function.
  What is the R code and its result?
```{r , include = TRUE}
    names(temp) <- city
       
    temp
```
 
  
   e. From the answer in d, what is the content of index 5 and index 6? What 
  is its R code?
```{r , include = TRUE}
    temp[5:6]
```
Using Matrices
\hfill\break   
2. Create a matrix of one to eight and eleven to fourteen with four columns
    #and three rows.
   
  a. What will be the R code for the #2 question and its result?   
```{r , include = TRUE}
    MATRIX <- matrix(c(1:8, 11:14), nrow = 3, ncol = 4)
    
    MATRIX
```
 
    
  b. Multiply the matrix by two. What is its R code and its result? 
```{r , include = TRUE}
    doubled_mtx <- MATRIX *2
   
    doubled_mtx
```
 
    
  c. What is the content of row 2? What is its R code?
```{r , include = TRUE}
    row_2 <- c(MATRIX[2,1], MATRIX[2,2], MATRIX[2,3], MATRIX[2,4])
    
    row_2
```
 
    
  d. What will be the R code if you want to display the column 3 and column 
  4 in row 1 and row 2? What is its output?
```{r , include = TRUE}
    row1_2 <- c(MATRIX[1, 3], MATRIX[1, 4], MATRIX[2, 3], MATRIX[2, 4])
    
    row1_2
```
 
  
  e. What is the R code is you want to display only the columns in 2 and 3, 
  row 3? What is its output?
```{r , include = TRUE}
    COLUMN2_3 <- c(MATRIX[3,2], MATRIX[3,3])
    COLUMN2_3
```

    
    
  f. What is the R code is you want to display only the columns 4? What is 
  its output? 
```{r , include = TRUE}
    COLUMN_4 <- c(MATRIX[1,4], MATRIX[2,4], MATRIX[3,4])
    COLUMN_4
```

   
  g. Name the rows as isa, dalawa, tatlo and columns as uno, dos, tres, 
  quatro for the matrix that was created in b.‘. What is its R code and 
  corresponding output?
```{r , include = TRUE}
    dimnames(MATRIX) <- list(c("isa", "dalawa", "tatlo"),
                            c("uno", "dos", "tres", "quatro"))
    MATRIX
```
  h. From the original matrix you have created in a, reshape the matrix by 
  assigning a new dimension with dim(). New dimensions should have 2 columns 
  and 6 rows. What will be the R code and its output?
```{r , include = TRUE}
    dim(MATRIX) <- c(6,2)
    MATRIX
```
Using Arrays
\hfill\break     
3. An array contains 1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1
```{r , include = TRUE}
    Array <- c(1, 2, 3, 6, 7, 8, 9, 0, 3, 4, 5, 1)
    Array
```
  
   
   a. Create an array for the above numeric values. Each values will be
   repeated twice # What will be the Rcode if you are to create a 
   three-dimensional array with 4 columns and 2 rows. What will be its output?
```{r , include = TRUE}
    Array1 <- array(rep(Array, 2), dim = c(2,4,3))
    Array1
```
  
     
  b. How many dimensions do your array have?
   
    ##it has 3 dimension
   
  c. Name the rows as lowercase letters and columns as uppercase letters 
  starting from the A. The array names should be “1st-Dimensional Array”, 
  “2nd-Dimentional Array”, and “3rd-Dimensional Array”. What will be the 
  R codes and its output?
```{r, include = TRUE}
    dimnames(Array1) <- list(letters[1:2], LETTERS[1:4], c("1st-Dimensional 
            Array", "2nd-Dimentional Array", "3rd-Dimensional Array"))
    Array1
```
  

