---
title: "RWorksheet_Callanga#5"
output:
  pdf_document: default
  html_document: default
date: "2022-11-23"
---

#a. Plot the data using a bar graph. Write the codes and copy the result.
```{r, include=TRUE}


  date1 <- c("1st", "2nd", "3rd", "4th")
  date2 <- c(80,75,70,60)

  graph<- barplot(date2, names.arg = date1, col = "red")
```

#b. Using the same table, label the barchart with
#Title = ” Enrollment of BS Computer Science
#horizontal axis = “Curriculum Year” and
#vertical axis = “number of students”
```{r, include=TRUE}


  graph<- barplot(date2, names.arg = date1, 
                main = "Enrollment of BS Computer Science", 
                ylab = "Number of Students", xlab = "Curriculum Year", 
                col = "red")
```

#2. The monthly income of De Jesus family was spent on the following:
#60% on Food, 10% on electricity, 5% for savings, and
#25% for other miscellaneous expenses.

#a. Create a table for the above scenario.
#Write the codes and its result.
```{r, include=TRUE}


  month_data <- data.frame(
    data = c("Food", "Electricity", "Savings", "Miscellaneous_expenses"),
    spent = c(60, 10, 5, 25)
  )
  month_data
  table_data <- table(month_data)
  table_data
```  


#b. Plot the data using a pie chart. Add labels, colors and legend.
#Write the codes and its result.
```{r, include=TRUE}


  pdata <- c( 60, 10, 5, 25)
  2
  data <- round(pdata/sum(pdata)*100,1)
  data <- paste(data, "%", sep = " ")
  
  piechart <- pie( pdata, labels = data, cex = 0.5, col = rainbow(4), main = 
                     "De Jesus family Monthly Expenses")
  legend("topright", c("Food", "Electricity", "Savings", "Miscellaneous"),
         cex = 0.5 , fill =rainbow(4))
```   

#3. Open the mtcars dataset.
```{r, include=TRUE}

 mtdata <- (mtcars$mpg)
 mtdata
``` 
 
#a. Create a simple histogram specifically for mpg (miles per gallon) variable.
#Use $ to select the mpg only. Write the codes and its result.
```{r, include=TRUE}


 hist(mtcars$mpg)
  
``` 

#b. Colored histogram with different number of bins.
```{r, include=TRUE}


 hist(mtcars$mpg, breaks=12, col="red")
```  

#c. Add a Normal Curve
```{r, include=TRUE}


  hwnc <-hist(mtdata, breaks=12, col="red", xlab="Miles Per Gallon",
              main="Histogram with Normal Curve")
  xfit<-seq(min(mtdata),max(mtdata),length=40)
  yfit<-dnorm(xfit,mean=mean(mtdata),sd=sd(mtdata))
  yfit <- yfit*diff(hwnc$mids[1:2])*length(mtdata)
  lines(xfit, yfit, col="blue", lwd=2)
```

#4. Open the iris dataset. Create a subset for each species.

#a. Write the codes and its result.
```{r, include=TRUE}

 
  dtf <- data.frame(iris)
  dtf
``` 
```{r, include=TRUE}


  setosa <- subset(iris, Species == "setosa")
  setosa
``` 
```{r, include=TRUE}


  versicolor <- subset(iris, Species == "versicolor")
  versicolor
```   
```{r, include=TRUE}


  virginica <- subset(iris, Species == "virginica")
  virginica
```  
#b. Get the mean for every characteristics of each species using colMeans().
#Write the codes and its result.
```{r, include=TRUE}


  setosa <- subset(iris, Species == "setosa")
  setosa <- colMeans(setosa[sapply(setosa,is.numeric)])
  setosa
```
```{r, include=TRUE}


  versicolor <- subset(iris, Species == "versicolor")
  versicolor <- colMeans(versicolor[sapply(versicolor,is.numeric)])
  versicolor
```
```{r, include=TRUE}


  virginica <- subset(iris, Species == "virginica")
  virginica <- colMeans(virginica[sapply(virginica,is.numeric)])
  virginica
```

#c. Combine all species by using rbind()
```{r, include=TRUE}


  rbtable <- rbind(setosa, versicolor, virginica)
  rbtable
```  

#d. From the data in 4-c: Create the barplot().
#Write the codes and its result.
```{r, include=TRUE}


  barplot(height = as.matrix(rbtable),main = "Iris Data",
          ylab = "Mean Scores",
          beside =T, col = rainbow(3)
  )
```
