---
title: "RWorksheet_Callanga#3b."
output:
  pdf_document: default
  html_document: default
date: "2022-11-23"
---
#1. Create a data frame using the table below.

#1) a. Write the codes.
```{r, include=TRUE}


data <- data.frame(
  Respondents = c(1:20),
  
  Sex = c(2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2, 2, 2, 2, 2, 2, 2, 1, 2),
  
  Fathers_Occupation = c(1, 3, 3, 3, 1, 2,  3, 1, 1, 1, 3, 2, 1, 3, 3, 1, 
                         3, 1, 2, 1),
  Persons_at_Home = c(5, 7, 3, 8, 5, 9, 6, 7, 8, 4, 7, 5, 4, 7, 8, 8,
                      3, 11, 7, 6),
  Siblings_at_School = c(6, 4, 4, 1, 2, 1, 5, 3, 1, 2, 3, 2, 5, 5, 2, 1,
                         2, 5, 3, 2),
  Types_of_Houses = c(1, 2, 3, 1, 1, 3, 3, 1, 2, 3, 2, 3, 2, 2, 3, 3, 3,
                      3, 3, 2)
)
  data
```  
#1) b.  Describe the data. Get the structure or the summary of the data
```{r, include=TRUE}
  
summary(data)

```
#1) c. Is the mean number of siblings attending is 5?
  #Answer: NO
  
#1) d.Extract the 1st two rows and then all the columns using the subsetting 
#  functions. Write the codes and its output.
```{r, include=TRUE}


  data1 <- subset(data[1:2, 1:6])
  data1
``` 
#1) e.Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.
  #functions. Write the codes and its output.
```{r, include=TRUE}

  data2 <- subset(data[c(3,5), c(2,4)])
  data2

```  
#1) f. Select the variable types of houses then store the vector that results 
  #as types_houses. Write the codes.
```{r, include=TRUE}
  
  data3 <- data$Types_of_Houses
  data3

```  
#1) g. Select only all Males respondent that their father occupation was farmer. 
#Write the codes and its output.
 
  #as types_houses.Write the codes.
  
```{r, include=TRUE}

  data4 <- subset(data[c(1:20), c(2,3)])
  data4
```  
```{r, include=TRUE}

  data5 <- data4[data$Fathers_Occupation == '1',]
  data5 

```
#1) h.  Select only all females respondent that have greater than or equal to 
  #5 number of siblings attending school. Write the codes and its outputs.
```{r, include=TRUE}


  data6 <- subset(data[c(1:20), c(2,5)])
  data6
```   
```{r, include=TRUE}


  data7 <- data6[data$Siblings_at_School >= '5',]
  data7
```   
#2. Write a R program to create an empty data frame. Using the following codes:

  
#2) Write a R program to create an empty data frame. Using the following 
  #codes:
```{r, include=TRUE}

 df = data.frame(Ints=integer(),
                  Doubles=double(), Characters=character(),
                  Logicals=logical(),
                  Factors=factor(),
                  stringsAsFactors=FALSE)
  print("Structure of the empty dataframe:")
  print(str(df))

```
#a. Describe the result
 
  #Answer: The result is an empty data frame. It has 0 column and 5    #rows, as for factor it has a 0 levels.
  
#3. Interpret the graph.
  
 #Answer: There are more negative comments than other comments.